%-------------------------
% Resume in Latex
% Author : Kevin Wagenheim
% Based off of: https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Kevin Wagenheim} \\ \vspace{1pt}
    \small 609-703-2946 $|$ \href{mailto:wagenheimk@me.com}{\underline{wagenheimk@me.com}} $|$ 
    \href{https://www.linkedin.com/in/kevinwagenheim/}{\underline{linkedin.com/in/kevinwagenheim}} $|$
    \href{https://github.com/Wagenheim/}{\underline{github.com/Wagenheim}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{Oct. 2025 -- Present}
      {ByDesign Technologies}{Tampa, FL}
      \resumeItemListStart
        \resumeItem{Develop and maintain full stack applications using Angular, AngularJS, Classic ASP, .NET, C\#, and MS SQL.}
        \resumeItem{Troubleshoot production bugs and implement new features across front-end and backend systems.}
        \resumeItem{Participate in modernizing CI/CD pipelines, supporting a transition to GitHub Actions and Octopus Deploy.}
        \resumeItem{Contribute to cloud migration initiatives, supporting the transition of on-premises workloads to cloud-based infrastructure.}
      \resumeItemListEnd

    \resumeSubheading
      {System and Cloud Administrator}{Jan. 2025 -- Sept. 2025}
      {Simple Syllabus}{Tampa, FL}
      \resumeItemListStart
        \resumeItem{Took ownership of AWS infrastructure in October 2023; officially promoted to System and Cloud Administrator in January 2025.}
        \resumeItem{Managed and deployed infrastructure using AWS services including RDS, ECS, EC2, Lambda, Batch, CloudFront, Step Functions, CloudWatch, and S3.}
        \resumeItem{Built the company’s first CI/CD pipeline using Bitbucket Pipelines, significantly reducing deployment time and errors.}
        \resumeItem{Owned on-call support and resolution of all production-level issues, from system outages to degraded performance.}
      \resumeItemListEnd

    \resumeSubheading
      {Full Stack Developer}{Apr. 2021 -- Jan. 2025}
      {Simple Syllabus}{Tampa, FL}
      \resumeItemListStart
        \resumeItem{Developed and maintained full stack applications using TypeScript, PHP, and PostgreSQL.}
        \resumeItem{Designed and integrated RESTful APIs, including third-party API integrations.}
        \resumeItem{Optimized complex SQL queries to improve data access speed and reduce load times.}
        \resumeItem{Built and optimized AngularJS components for the front end, resolving performance issues and bugs.}
        \resumeItem{Participated in Agile sprints and planning sessions using Jira, collaborating with cross-functional teams.}
    \resumeItemListEnd

    \resumeSubheading
      {Web Application Developer Trainee}{Apr. 2020 -- July 2020}
      {Revature}{Tampa, FL}
      \resumeItemListStart
        \resumeItem{Trained in full stack development and cloud deployment workflows using Java, TypeScript, SQL, and AWS.}
        \resumeItem{Created APIs using Springboot and front-end interfaces using ReactJS.}
        \resumeItem{Deployed applications to the cloud using AWS.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AWS Certified Cloud Practitioner}{December 2023}
      {Credential ID: 968GCF1L5JE41457}{}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Tampa}{Tampa, FL}
      {Bachelor of Science in Mathematics}{Aug. 2015 -- May 2019}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
% \section{Projects}
%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%           {\textbf{Palworld Server Discord Bot} $|$ \emph{TypeScript, NodeJS, AWS EC2}}{June 2020 -- Present}
%           \resumeItemListStart
%             \resumeItem{Utilized Discord's node package to create a Discord bot to manage a Palworld multiplayer server.}
%             \resumeItem{Deployed the bot and server on AWS EC2 instances.}
%             \resumeItem{Created automated backups of the server files in AWS S3.}
%             \resumeItem{Abstracted commands and errors to follow OOP best practices.}
%             \resumeItem{Minimized cost of running the application to keep it under \$50}
%           \resumeItemListEnd
%     \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages/Frameworks}{: TypeScript, JavaScript, C\#, .NET, PHP, Angular/AngularJS, Classic ASP} \\
     \textbf{Cloud \& Infrastructure}{: AWS (EC2, ECS, RDS, Lambda, S3, CloudFront, Step Function, Cloudwatch), Cloud Migration, Linux (Ubuntu)} \\
     \textbf{DevOps \& CI/CD}{: Docker, Bitbucket Pipelines, Github Actions, TeamCity, Octopus Deploy} \\
     \textbf{Databases}{: PostgreSQL, Microsoft SQL Server} \\
     \textbf{Tools}{: Bash, Git, Jira, Agile/Scrum, Postman}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}